Ethereum: A Secure Decentralised Generalised Transaction Ledger

### 2014-04-17 Paper.tex
Other minor fixes.

\begin{description}
\item[nonce] A scalar value equal to the number of transactions sent from this address, or, in the case of contract accounts, the number of contract-creations made by this account.
\item[balance] A scalar value equal to the number of wei owned by this address.
\item[stateRoot] A 256-bit hash equal to the root node of a further trie structure that encodes the storage contents of the contract. Though a separate data structure, this trie is still stored using the same underlying state database. This trie takes the form as a simple mapping between domains of 256-bit values.
\item[codeHash] The hash of the EVM code of this contract---this is the code that gets executed should this address reveive a call; it is immutable and thus, unlike all other fields, cannot be changed after construction. All such code fragments are contained in the state database under their corresponding hashes for later retrieval.
\end{description}

@@

\begin{description}
\item[nonce] A scalar value equal to the number of transactions sent by the sender; formally $T_n$.
\item[value] A scalar value equal to the number of wei to be transferred to the message call's recipient or, in the case of contract creation, as an endowment to the newly created contract's account; formally $T_v$.
\item[gasPrice] A scalar value equal to the number of wei to be paid per unit of gas for all computation costs incurred as a result of the execution of this transaction; formally $T_p$.
\item[gasLimit] A scalar value equal to the maximum amount of gas that should be used in executing this transaction. This is paid up-front, before any computation is done and may not be topped-up later; formally $T_g$.
\item[to] The 160-bit address of the message call's recipient or the zero address for a contract-creation transaction; formally $T_r$.
\item[v, r, s] Three scalar values corresponding to the signature of the transaction and used to determine the sender of the transaction.
\end{description}

@@

\begin{description}
\item[parentHash] The SHA3 256-bit hash of the parent block, in its entirety; formally $H_p$.
\item[unclesHash] The SHA3 256-bit hash of the uncles list portion of this block; formally $H_u$.
\item[coinbase] The 160-bit address to which all fees collected from the successful mining of this block be transferred; formally $H_b$.
\item[stateRoot] The SHA3 256-bit hash of the root node of the state trie, after all transactions are executed and finalisations applied; formally $H_r$.
\item[transactionsHash] The SHA3 256-bit hash of the transactions list portion of this block; formally $H_t$.
\item[difficulty] A scalar value corresonding to the difficulty level of this block. This can be calculated from the previous block's difficulty level and the timestamp; formally $H_d$.
\item[timestamp] A scalar value equal to the reasonable output of Unix's time() at this block's inception; formally $H_s$.
\item[extraData] An arbitrary byte array containing data relavant to this block. Generally 256-bit or less, but could be much larger in the genesis block. Not formally used.
\item[nonce] A 256-bit hash which proves that a sufficient amount of computation has been carried out on this block; formally $H_n$.
\end{description}

>>>>

\begin{description}
\item[nonce] A scalar value equal to the number of transactions sent from this address, or, in the case of contract accounts, the number of contract-creations made by this account.
\item[balance] A scalar value equal to the number of wei owned by this address.
\item[stateRoot] A 256-bit hash equal to the root node of a further trie structure that encodes the storage contents of the contract. Though a separate data structure, this trie is still stored using the same underlying state database. This trie takes the form as a simple mapping between domains of 256-bit values.
\item[codeHash] The hash of the EVM code of this contract---this is the code that gets executed should this address receive a message call; it is immutable and thus, unlike all other fields, cannot be changed after construction. All such code fragments are contained in the state database under their corresponding hashes for later retrieval.
\end{description}

@@

\begin{description}
\item[nonce] A scalar value equal to the number of transactions sent by the sender; formally $T_n$.
\item[value] A scalar value equal to the number of wei to be transferred to the message call's recipient or, in the case of contract creation, as an endowment to the newly created contract's account; formally $T_v$.
\item[gasPrice] A scalar value equal to the number of wei to be paid per unit of gas for all computation costs incurred as a result of the execution of this transaction; formally $T_p$.
\item[gasLimit] A scalar value equal to the maximum amount of gas that should be used in executing this transaction. This is paid up-front, before any computation is done and may not be topped-up later; formally $T_g$.
\item[to] The 160-bit address of the message call's recipient or the zero address for a contract-creation transaction; formally $T_r$.
\item[v, r, s] A scalar and complex value corresponding to the signature of the transaction and used to determine the sender of the transaction; formally $T_v$ and $T_{rs}$. This is expanded in Appendix \ref{app:signing}.
\end{description}

@@

\begin{description}
\item[parentHash] The SHA3 256-bit hash of the parent block, in its entirety; formally $H_p$.
\item[unclesHash] The SHA3 256-bit hash of the uncles list portion of this block; formally $H_u$.
\item[coinbase] The 160-bit address to which all fees collected from the successful mining of this block be transferred; formally $H_b$.
\item[stateRoot] The SHA3 256-bit hash of the root node of the state trie, after all transactions are executed and finalisations applied; formally $H_r$.
\item[transactionsHash] The SHA3 256-bit hash of the transactions list portion of this block; formally $H_t$.
\item[difficulty] A scalar value corresonding to the difficulty level of this block. This can be calculated from the previous block's difficulty level and the timestamp; formally $H_d$.
\item[timestamp] A scalar value equal to the reasonable output of Unix's time() at this block's inception; formally $H_s$.
\item[extraData] An arbitrary byte array containing data relavant to this block. With the exception of the genesis block, this must be 32 bytes or fewer. Not formally used.
\item[nonce] A 256-bit hash which proves that a sufficient amount of computation has been carried out on this block; formally $H_n$.
\end{description}
